---
title: Dashboard
author: Tiffany Gonzalez
date: '2017-09-29'
slug: dashboard
categories:
  - R
tags:
  - Lahman
  - dplyr
  - ggplot2
  - ggiraph
  - flexdashboard
---

##Dashboards are a great way to organize and present information that is easy to read on one given page or site. A dashboard is an interactive tool that allows the user to visualize large amounts of data.

To set up our dashboard we need to bring in our packages, and this time we will be adding the new package to set the dashboard up called, flexdashboard.

```{r setup, include=FALSE}
library(flexdashboard)
library(Lahman)
library(dplyr)
library(ggplot2)

result<-Batting%>%
  filter(playerID=='ruthba01')%>%
  select(yearID,SO,HR)
```

The first graph shown is a scatterplot: 

```{r}
ggplot()+
  geom_point(data=result,aes(x=SO,y=HR))+
  xlab("Strikeouts")+
  ylab("Homeruns")
```

This graph is a histogram:

```{r}
ggplot()+
  geom_histogram(data=result,aes(x=HR),bins=5, color="blue",fill="white")+
  xlab("Homeruns")
```

This is a combination of a scatterplot and line graph: 

```{r}
ggplot()+
  geom_point(data=result,aes(x=yearID,y=HR))+
  geom_line(data=result,aes(x=yearID,y=HR))+
  xlab("Year")+
  ylab("Homeruns")
```

Once our graphs are created and ready, our dashboard can now be built. 

Since dashboards are not very compatible with a blog post, you can find the dashboard on my Github page, by clicking [here](https://tgonza75.github.io/dashboard/) 
