---
title: Article
author: Tiffany Gonzalez
date: '2017-11-14'
categories:
  - R
tags:
  - dplyr
  - tm
  - tidytext
  - wordcloud
  - stringr
  - gutenbergr
  - knitr
---

In this post, we will be learning how to use LaTeX to crete an article. We first need to import our libraries we will be using:

```{r setup, include=FALSE}
library(tidytext)
library(gutenbergr)
library(stringr)
library(dplyr)
library(wordcloud)
library(knitr)
```

# Creating the Wordcloud for the article

As shown previously in the "Wordcloud" post from my blog, we went through the steps for showing how to make a wordcloud... I willl briefly explain throughout the codes what we went over.

```{r setup, include=FALSE }
# Finding the book Peter Pan within the gutenbergr database

gutenberg_works(str_detect(title,'Peter Pan'))

peter_pan<-gutenberg_download(39755)

```


```{r}
# Splitting each line of text into words

words_df<-peter_pan%>%
  unnest_tokens(word,text)

words_df
```



```{r}
# Getting rid of any common words

words_df<-words_df%>%
  filter(!word %in% stop_words$word)

words_df
```


```{r}
# Count how many times each word appears

word_freq<-words_df%>%
  group_by(word)%>%
  summarize(count=n())

word_freq
```


```{r}
# Creating the final product

wordcloud(word_freq$word,word_freq$count,min.freq=8)
```

#Creating the Article

We will use a new document type, R Sweave. This will give a basic structure of the article we will be making.The file pops up a template shown as:

documentclass{article}

begin{document}

end{document}


In between our beginning and end of the document is where we will put our content for the entire article. This is where we will put our code for the wordcloud we want to build.

First We want to create a title and show the author. We will do this by putting the following tags after the begin{document}

title{Peter Pan Wordcloud}
author{Tiffany Gonzalez}
maketitle

We can then begin and end an {abstract} as well as {section} like we did with the {document}


You can see my article, fully compiled [here](file:///C:/Users/ttmg125/Desktop/peterpan/article.pdf)
